Democracy, Public Support, and Measurement Uncertainty

### 2021-07-31 paper/dcpo_demsupport.Rmd
correct variable and model lables.

#df_pure_clsAjps <- purrr::map(1:900, function(anEntry) {
#  correct_cls_ajps[[anEntry]] %>% 
#    plm::pdata.frame(index = c("country", "year"))
#})

#result_pure_clsUncertain  <- map(ls_mod_ajpsCLS[1:2], function(aMod){
#  result <- methodComposition1(df_pure_clsAjps,aMod)
#})

#names(result_pure_clsUncertain) <- c("pooled", "pooled-regime")

#result_pure_clsUncertain_gmm  <- map(ls_mod_ajpsCLS[3:4], function(aMod){
#  result <- methodComposition2(df_pure_clsAjps,aMod)
#})
#names(result_pure_clsUncertain_gmm) <- c("gmm", "gmm-regime")

#mocresult_pureAJPS <- append(result_pure_clsUncertain, result_pure_clsUncertain_gmm)

#saveRDS(mocresult_pureAJPS, file =here("output","estimates_moc_pureAJPS.RDS"))

@@

plot_AJPS1 <- dwplot(result_pooledAJPS, dodge_size = 0.8, by_2sd = FALSE) +
  scale_y_discrete(labels = parse(text = levels(terms))) +
  labs(
    title = "DV: V-Dem Liberal Democracy Index",
    subtitle = "Regime Compacted"
  ) +
  facet_wrap(~type, scales = "free_x") + 
  theme(legend.position = "none")

@@

result_regimeAJPS <- bind_rows(result_regime, result_regimeGmm) %>%
  filter(term != "(Intercept)") %>%
  mutate(
    term = rep(
      c("Democracy\n (t-1)",
        "Democracy\n (t-2)",
        "Support\n demo only\n (t-1)",
        "Support\n auto only\n (t-1)",
        "Log GDP\n per capita\n (t-1)",
        "GDP per\n capita growth\n (t-1)",
        "Regional\n democracy\n (t-1)",
        "Percent\n Muslim\n (t-1)",
        "Resource\n dependence\n (t-1)"),
      time = 6), 
    type = factor(type, levels = c("Pooled", "GMM")),
    model = factor(model, levels = c("Original","Uncertainty+Corrected", "Uncertainty+Expanded Data")))
terms2 <- factor(rev(c("Democracy[t-1]",
                       "Democracy[t-2]",
                       "Support[t-1] (democracies~only)",
                       "Support[t-1] (autocracies~only)",
                       "Log~GDP~per~capita[t-1]",
                       "GDP~per~capita~growth[t-1]",
                       "Regional~democracy[t-1]",
                       "Percent~Muslim[t-1]",
                       "Resource~dependence[t-1]")), levels =
                   rev(c("Democracy[t-1]",
                         "Democracy[t-2]",
                         "Support[t-1] (democracies~only)",
                         "Support[t-1] (autocracies~only)",
                         "Log~GDP~per~capita[t-1]",
                         "GDP~per~capita~growth[t-1]",
                         "Regional~democracy[t-1]",
                         "Percent~Muslim[t-1]",
                         "Resource~dependence[t-1]")))
plot_AJPS2 <- dwplot(result_regimeAJPS, dodge_size = 0.8, by_2sd = FALSE) +
  scale_y_discrete(labels = parse(text = levels(terms2))) +
  labs(
    title = "",
    subtitle = "Regime Specific"
  ) +
  facet_wrap(~type, scales = "free_x") +
  theme(legend.position = "bottom", 
        legend.title = element_blank())
legend <- get_legend(plot_AJPS2)
plot_AJPS2 <- plot_AJPS2 + theme(legend.position = "none")
grid.arrange(plot_AJPS1, plot_AJPS2, legend, ncol = 1)

@@

#df_pure_clsAPSR <- purrr::map(1:900, function(anEntry) {
#  correct_cls_apsr[[anEntry]] %>% 
#    plm::pdata.frame(index = c("country", "year"))
#}
#)

#mocresult_pureAPSR  <- map(ls_mod_apsrCLS, function(aMod){
#  result <- methodComposition3(df_pure_clsAPSR,aMod)
#})

#names(mocresult_pureAPSR) <- c("pooled1", "pooled-regime1", "pooled2", "pooled-regime2",
#                                "fd1", "fd-regime1", "fd2", "fd-regime2")

#saveRDS(mocresult_pureAPSR, file = here::here("ouput","estimates_moc_pureAPSR.RDS"))

@@

#df_exp_clsAPSR <- purrr::map(1:900, function(anEntry) {
#  expcor_cls_apsr[[anEntry]] %>% 
#    plm::pdata.frame(index = c("country", "year"))
#}
#)

#mocresult_expAPSR <- map(ls_mod_apsrCLS, function(aMod){
 # result <- methodComposition3(df_exp_clsAPSR,aMod)
#})

#names(mocresult_expAPSR) <- c("pooled1", "pooled-regime1", "pooled2", "pooled-regime2",
#                                "fd1", "fd-regime1", "fd2", "fd-regime2")
#saveRDS(mocresult_expAPSR, file = here::here("ouput","estimates_moc_expAPSR.RDS"))

@@

terms1 <- factor(rev(c("Support[t-1]",
                       "Support[t-2]",
                       "Delta~Liberal~democracy",
                       "Liberal~democracy[t-1]",
                       "Delta~Log~GDP~per~capita",
                       "Log~GDP[t-1]")),
                 levels = rev(c("Support[t-1]",
                                "Support[t-2]",
                                "Delta~Liberal~democracy",
                                "Liberal~democracy[t-1]",
                                "Delta~Log~GDP~per~capita",
                                "Log~GDP[t-1]")))
plot_APSR1 <- dwplot(result_APSR1, dodge_size = 0.8, by_2sd = FALSE) +
  scale_y_discrete(labels = parse(text = levels(terms1))) +
  labs(
    title = "DV: The Change of Public Support for Democracy",
    subtitle = "Regime Compacted"
  ) +
  facet_wrap(~type, drop=T,scales = "free_x") +
  theme(legend.position = "none")

@@

result_RegAPSR1 <- bind_rows(result_ecmReg1, result_fdReg1) %>%
  filter(term != "(Intercept)") %>%
  mutate(
    term = c(rep(
      c("Democratic Mood\n (t-1)",
        "Democratic Mood\n (t-2)",
        "Electoral Democracy\n (Difference)",
        "Electoral Democracy\n (t-1)",
        "Minoritarian Democracy\n (Difference)",
        "Minoritarian Democracy\n (t-1)",
        "Log GDP\n per capita\n (Difference)",
        "Log GDP\n (t-1)"),
      time = 3),
      rep(
        c("Electoral Democracy\n (Difference)", 
          "Minoritarian Democracy\n (Difference)",
          "Log GDP\n per capita\n (Difference)"), 
        time = 3
      )),
    type = factor(type,  levels = c("ECM", "First Difference")),
    model = factor(model, levels = c("Original","Uncertainty+Corrected", "Uncertainty+Expanded Data"))
  )
terms3 <- factor(rev(c("Support[t-1]",
                       "Support[t-2]",
                       "Delta~Electoral~democracy",
                       "Electoral~democracy[t-1]",
                       "Delta~Minoritarian~democracy",
                       "Minoritarian~democracy[t-1]",
                       "Delta~Log~GDP~per~capita",
                       "Log~GDP[t-1]")),
                 levels = rev(c("Support[t-1]",
                                "Support[t-2]",
                                "Delta~Electoral~democracy",
                                "Electoral~democracy[t-1]",
                                "Delta~Minoritarian~democracy",
                                "Minoritarian~democracy[t-1]",
                                "Delta~Log~GDP~per~capita",
                                "Log~GDP[t-1]")))
plot_RegAPSR1 <- dwplot(result_RegAPSR1, dodge_size = 0.8, by_2sd = FALSE) +
  scale_y_discrete(labels = parse(text = levels(terms3))) +
  labs(
    title = "",
    subtitle = "Regime Specified"
  ) +
  facet_wrap(~type, scales = "free_x") + 
  theme(legend.position = "none")

@@

result_RegAPSR2 <- bind_rows(result_ecmReg2, result_fdReg2) %>%
  filter(term != "(Intercept)") %>%
  mutate(
    term = c(rep(
      c("Democratic Mood\n (t-1)",
        "Democratic Mood\n (t-2)",
        "Electoral Democracy\n (Difference)",
        "Electoral Democracy\n (t-1)",
        "Minoritarian Democracy\n (Difference)",
        "Minoritarian Democracy\n (t-1)",
        "Log GDP\n per capita\n (Difference)",
        "Log GDP\n (t-1)",
        "Corruption\n (Difference)",
        "Corruption\n (t-1)"
      ),
      time = 3),
      rep(
        c("Electoral Democracy\n (Difference)", 
          "Minoritarian Democracy\n (Difference)",
          "Log GDP\n per capita\n (Difference)",
          "Corruption\n (Difference)"), 
        time = 3
      )),
    type = factor(type,  levels = c("ECM", "First Difference")),
    model = factor(model, levels = c("Original","Uncertainty+Corrected", "Uncertainty+Expanded Data"))
  )
terms4 <- factor(rev(c("Support[t-1]",
                       "Support[t-2]",
                       "Delta~Electoral~democracy",
                       "Electoral~democracy[t-1]",
                       "Delta~Minoritarian~democracy",
                       "Minoritarian~democracy[t-1]",
                       "Delta~Log~GDP",
                       "Log~GDP[t-1]",
                       "Delta~Corruption",
                       "Corruption[t-1]")),
                 levels = rev(c("Support[t-1]",
                                "Support[t-2]",
                                "Delta~Electoral~democracy",
                                "Electoral~democracy[t-1]",
                                "Delta~Minoritarian~democracy",
                                "Minoritarian~democracy[t-1]",
                                "Delta~Log~GDP",
                                "Log~GDP[t-1]",
                                "Delta~Corruption",
                                "Corruption[t-1]")))
plot_RegAPSR2 <- dwplot(result_RegAPSR2, dodge_size = 0.8, by_2sd = FALSE) +
  scale_y_discrete(labels = parse(text = levels(terms4))) +
  labs(
    title = "",
    subtitle = "Regime Specified w. Corruption"
  ) +
  facet_wrap(~type, scales = "free_x") +
  theme(legend.position = "bottom", 
        legend.title = element_blank())

>>>>

@@

plot_AJPS1 <- dwplot(result_pooledAJPS, dodge_size = 0.8, by_2sd = FALSE) +
  scale_y_discrete(labels = parse(text = levels(terms))) +
  labs(
    title = "DV: V-Dem Liberal Democracy Index",
    subtitle = "Pooled"
  ) +
  facet_wrap(~type, scales = "free_x") + 
  theme(legend.position = "none")

@@

result_regimeAJPS <- bind_rows(result_regime, result_regimeGmm) %>%
  filter(term != "(Intercept)") %>%
  mutate(
    term = rep(
      c("Democracy\n (t-1)",
        "Democracy\n (t-2)",
        "Support\n demo only\n (t-1)",
        "Support\n auto only\n (t-1)",
        "Log GDP\n per capita\n (t-1)",
        "GDP per\n capita growth\n (t-1)",
        "Regional\n democracy\n (t-1)",
        "Percent\n Muslim\n (t-1)",
        "Resource\n dependence\n (t-1)"),
      time = 6), 
    type = factor(type, levels = c("Pooled", "GMM")),
    model = factor(model, levels = c("Original","Uncertainty+Corrected", "Uncertainty+Expanded Data")))
terms2 <- factor(rev(c("Democracy[t-1]",
                       "Democracy[t-2]",
                       "Support[t-1] (democracies~only)",
                       "Support[t-1] (autocracies~only)",
                       "Log~GDP~per~capita[t-1]",
                       "GDP~per~capita~growth[t-1]",
                       "Regional~democracy[t-1]",
                       "Percent~Muslim[t-1]",
                       "Resource~dependence[t-1]")), levels =
                   rev(c("Democracy[t-1]",
                         "Democracy[t-2]",
                         "Support[t-1] (democracies~only)",
                         "Support[t-1] (autocracies~only)",
                         "Log~GDP~per~capita[t-1]",
                         "GDP~per~capita~growth[t-1]",
                         "Regional~democracy[t-1]",
                         "Percent~Muslim[t-1]",
                         "Resource~dependence[t-1]")))
plot_AJPS2 <- dwplot(result_regimeAJPS, dodge_size = 0.8, by_2sd = FALSE) +
  scale_y_discrete(labels = parse(text = levels(terms2))) +
  labs(
    title = "",
    subtitle = "Regime Specified"
  ) +
  facet_wrap(~type, scales = "free_x") +
  theme(legend.position = "bottom", 
        legend.title = element_blank())
legend <- get_legend(plot_AJPS2)
plot_AJPS2 <- plot_AJPS2 + theme(legend.position = "none")
grid.arrange(plot_AJPS1, plot_AJPS2, legend, ncol = 1)

@@

@@

@@

terms1 <- factor(rev(c("Support[t-1]",
                       "Support[t-2]",
                       "Delta~Liberal~democracy",
                       "Liberal~democracy[t-1]",
                       "Delta~Log~GDP~per~capita",
                       "Log~GDP[t-1]")),
                 levels = rev(c("Support[t-1]",
                                "Support[t-2]",
                                "Delta~Liberal~democracy",
                                "Liberal~democracy[t-1]",
                                "Delta~Log~GDP~per~capita",
                                "Log~GDP[t-1]")))
plot_APSR1 <- dwplot(result_APSR1, dodge_size = 0.8, by_2sd = FALSE) +
  scale_y_discrete(labels = parse(text = levels(terms1))) +
  labs(
    title = "DV: The Change of Public Support for Democracy",
    subtitle = "Pooled"
  ) +
  facet_wrap(~type, drop=T,scales = "free_x") +
  theme(legend.position = "none")

@@

result_RegAPSR1 <- bind_rows(result_ecmReg1, result_fdReg1) %>%
  filter(term != "(Intercept)") %>%
  mutate(
    term = c(rep(
      c("Democratic Mood\n (t-1)",
        "Democratic Mood\n (t-2)",
        "Electoral Democracy\n (Difference)",
        "Electoral Democracy\n (t-1)",
        "Minoritarian Democracy\n (Difference)",
        "Minoritarian Democracy\n (t-1)",
        "Log GDP\n per capita\n (Difference)",
        "Log GDP\n (t-1)"),
      time = 3),
      rep(
        c("Electoral Democracy\n (Difference)", 
          "Minoritarian Democracy\n (Difference)",
          "Log GDP\n per capita\n (Difference)"), 
        time = 3
      )),
    type = factor(type,  levels = c("ECM", "First Difference")),
    model = factor(model, levels = c("Original","Uncertainty+Corrected", "Uncertainty+Expanded Data"))
  )
terms3 <- factor(rev(c("Support[t-1]",
                       "Support[t-2]",
                       "Delta~Electoral~democracy",
                       "Electoral~democracy[t-1]",
                       "Delta~Minoritarian~democracy",
                       "Minoritarian~democracy[t-1]",
                       "Delta~Log~GDP~per~capita",
                       "Log~GDP[t-1]")),
                 levels = rev(c("Support[t-1]",
                                "Support[t-2]",
                                "Delta~Electoral~democracy",
                                "Electoral~democracy[t-1]",
                                "Delta~Minoritarian~democracy",
                                "Minoritarian~democracy[t-1]",
                                "Delta~Log~GDP~per~capita",
                                "Log~GDP[t-1]")))
plot_RegAPSR1 <- dwplot(result_RegAPSR1, dodge_size = 0.8, by_2sd = FALSE) +
  scale_y_discrete(labels = parse(text = levels(terms3))) +
  labs(
    title = "",
    subtitle = "Institution Specified"
  ) +
  facet_wrap(~type, scales = "free_x") + 
  theme(legend.position = "none")

@@

result_RegAPSR2 <- bind_rows(result_ecmReg2, result_fdReg2) %>%
  filter(term != "(Intercept)") %>%
  mutate(
    term = c(rep(
      c("Democratic Mood\n (t-1)",
        "Democratic Mood\n (t-2)",
        "Electoral Democracy\n (Difference)",
        "Electoral Democracy\n (t-1)",
        "Minoritarian Democracy\n (Difference)",
        "Minoritarian Democracy\n (t-1)",
        "Log GDP\n per capita\n (Difference)",
        "Log GDP\n (t-1)",
        "Corruption\n (Difference)",
        "Corruption\n (t-1)"
      ),
      time = 3),
      rep(
        c("Electoral Democracy\n (Difference)", 
          "Minoritarian Democracy\n (Difference)",
          "Log GDP\n per capita\n (Difference)",
          "Corruption\n (Difference)"), 
        time = 3
      )),
    type = factor(type,  levels = c("ECM", "First Difference")),
    model = factor(model, levels = c("Original","Uncertainty+Corrected", "Uncertainty+Expanded Data"))
  )
terms4 <- factor(rev(c("Support[t-1]",
                       "Support[t-2]",
                       "Delta~Electoral~democracy",
                       "Electoral~democracy[t-1]",
                       "Delta~Minoritarian~democracy",
                       "Minoritarian~democracy[t-1]",
                       "Delta~Log~GDP",
                       "Log~GDP[t-1]",
                       "Delta~Corruption",
                       "Corruption[t-1]")),
                 levels = rev(c("Support[t-1]",
                                "Support[t-2]",
                                "Delta~Electoral~democracy",
                                "Electoral~democracy[t-1]",
                                "Delta~Minoritarian~democracy",
                                "Minoritarian~democracy[t-1]",
                                "Delta~Log~GDP",
                                "Log~GDP[t-1]",
                                "Delta~Corruption",
                                "Corruption[t-1]")))
plot_RegAPSR2 <- dwplot(result_RegAPSR2, dodge_size = 0.8, by_2sd = FALSE) +
  scale_y_discrete(labels = parse(text = levels(terms4))) +
  labs(
    title = "",
    subtitle = "Institution Specified w. Corruption"
  ) +
  facet_wrap(~type, scales = "free_x") +
  theme(legend.position = "bottom", 
        legend.title = element_blank())
